Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-02 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex

\section{Human-Centered IEC Framework}
\label{sec:framework}
% Comment: 
% Maybe in this case we should use the term software framework or architecture. 
The general goal of this line of research is to develop a human-centered \cite{gasson2003human} 
software framework for interactive evolutionary computation (IEC). 
A framework is defined as a reusable architectural design together
with an implementation \cite{campbell1991choices}, in this case 
providing generalized components to developers of IEC systems. In the
description %below? If that's te chase, we _will_ - JJ
 we deliberately use the more general 
term Human instead of User, because humans are not always playing the role of users in software engineering sense, they
could just be interacting naturally with their environment and
unwittingly and at the same time they are implicitly
evaluating a possible solution.

%Which framework? Are we talking about a particular framework or that
%is the general rule for frameworks? - JJ
The framework includes components that can be refined to increase
participation and also to minimize the amount of evaluations needed for the evolutionary process in a given IEC application. Software frameworks often have a vison or a way of thinking \cite{carneiro2010introducing} guiding their
design. Before diving into details the main design decisions of the
framework are explained next:  % constraints? Rules? You don't decide
                               % that users are humans, they simply
                               % are - JJ

>>>>

\section{Human-Centered IEC Framework}
\label{sec:framework}
% Comment: 
% Maybe in this case we should use the term software framework or architecture. 
The general goal of this line of research is to develop a human-centered \cite{gasson2003human} 
software framework for interactive evolutionary computation (IEC). 
A framework is defined as a reusable architectural design together
with an implementation \cite{campbell1991choices}, in this case 
providing generalized components to developers of IEC systems. In the
description below %below? If that's te chase, we _will_ - JJ
% Not only in the description, more like a paradigm shitf. But ok for now - Mario
 we will deliberately use the more general 
term Human instead of User, because humans are not always playing the role of users in software engineering sense, they
could just be interacting naturally with their environment and
unwittingly and at the same time they are implicitly
evaluating a possible solution.

%Which framework? Are we talking about a particular framework or that
%is the general rule for frameworks? - JJ
%Is general bu I was talking about this one - Mario
The proposed framework includes components that can be refined to increase
participation and also to minimize the amount of evaluations needed for the evolutionary 
process in a given IEC application. Software frameworks often have a vison or a way 
of thinking \cite{carneiro2010introducing} guiding their
design. Before diving into details the main design decisions of the
framework are explained next:  % constraints? Rules? You don't decide
                               % that users are humans, they simply
                               % are - JJ 
                               % Ok, is more like we want to acknowledge that, 
                               % To Do - Mario
